GMSE: a general tool for management strategy evaluation

### 2017-09-14 notebook/presentation/GMSE_presentation.Rmd
More on geese

- Use some data from Jeremy's paper?

>>>>

- Wild geese declined starting in the 1930s, likely caused by habitat loss and increased hunting
- Refuges were established and hunting restricted in the 1950s, leading to recovery
- Since the 1960s, many populations have exponentially increased
- Population growth coincides with a switch from natural wetlands to agricultural landscapes
- Switch to agricultural exploitation causes conflict with farmers

[Fox & Madsen 2017 *Ambio* **46(s2)**:170-187](http://doi.org/10.1007/s13280-016-0878-2)
[Fox & Abraham 2017 *Ambio* **46(s2)**:188-197](http://doi.org/10.1007/s13280-016-0879-1)
